\vspace{-1cm} Model linearity breeds contempt: using non-linear models to uncover general biogeographical patterns

### 2021-03-02 manuscript/manuscript.tex
Preparing binomial models

\subsubsection*{Sampling the posterior}
We generated the posterior samples for the Bayesian models with the Hamiltonian Monte Carlo algorithm implementation provided by the R package `rstan' to \citep{standevelopentteamRStanInterfaceStan2021}. Sampling models like the ones described above can be computationally very expensive. This is especially true when using ordered categorical likelihood functions (see \citealt{standevelopmentteamStanModelingLanguage2021}). Therefore, we focus on those species for which we have more than 10 occurrences when modelling binary data, which is the case for the majority of the results of this work. When using ordinal data, we limit our study to those species for which have more than 50 occurrences.

>>>>

\subsubsection*{Sampling the posterior}
We generated the posterior samples for the Bayesian models with the Hamiltonian Monte Carlo algorithm implementation provided by the R package `rstan' to \citep{standevelopentteamRStanInterfaceStan2021}. Sampling models like the ones described above can be computationally very expensive. This is especially true when using ordered categorical likelihood functions (see \citealt{standevelopmentteamStanModelingLanguage2021}). Therefore, we focus on those species for which we have at least 10 occurrences when modelling binary data, which is the case for the majority of the results of this work. When using ordinal data, we limit our study to those species for which have more than 50 occurrences.
% A random subset of a 100 species of those with at least 10 occurrences.
